Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling

### 2024-12-12 presentation/backup.tex
slide edits

\begin{frame}[noframenumbering]
  \frametitle{Backward-Facing Step Flow Validation Test Results}
  \begin{columns}
    \column{11.5cm}
    \begin{figure}[htb]
      \centering
      \hfill
      \begin{subfigure}[t]{0.24\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{bfs_downstream_vel}
        \caption{Normalized velocity distributions downstream of step.}
        \label{fig:bfs-downstream}
      \end{subfigure} %\hfill \\
  %    \centering
      \hfill
      \begin{subfigure}[t]{0.24\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{bfs_cf}
        \caption{Skin friction coefficient along the bottom wall.}
        \label{fig:bfs-cf}
      \end{subfigure}
      \hfill
      \begin{subfigure}[t]{0.24\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{bfs_cp}
        \caption{Skin pressure coefficient along the bottom wall.}
        \label{fig:bfs-cp}
      \end{subfigure}% \hfill \\
  %    \centering
      \begin{subfigure}[t]{0.24\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{bfs_stress}
        \caption{Normalized turbulent shear stress downstream
        of step.}
        \label{fig:bfs-stress}
      \end{subfigure}
      \caption{Comparison of backward facing step flow results against reference
      experimental data and computational data from CFL3D. $x/H$ values are normalized horizontal
      distances relative to the step.}
      \label{fig:bfs-plots}
    \end{figure}
  \end{columns}
  \begin{itemize}
    \item Minor discrepancies between numerical and experimental data typical of RANS-based turbulence models.
    \item Moltres provides better predictments along $x/H=1$ than CFL3D.
  \end{itemize}
\end{frame}

@@

@@

@@

@@

@@

>>>>

\begin{frame}[noframenumbering]
  \frametitle{Backward-Facing Step Flow Validation Test Setup}
  \begin{columns}
    \column{5.5cm}
    \begin{figure}[h]
      \centering
      \includegraphics[width=\columnwidth]{backstep-geom-pres}
      \caption{Backward step geometry for the turbulent BFS flow verification test. The red box indicates
      the region shown by the close-up view in Figure \ref{fig:bfs-mesh}.}
      \label{fig:backstep-geom}
    \end{figure}
    \column{5.5cm}
    \begin{figure}[h]
      \centering
      \includegraphics[width=\columnwidth]{bfs_mesh}
      \caption{Close-up view of the mesh for the BFS flow test. The step is situated at $x=110$ m
      with a height of $H=1$ m.}
      \label{fig:bfs-mesh}
    \end{figure}
  \end{columns}
\end{frame}

@@

\begin{frame}[noframenumbering]
  \frametitle{1-D Neutronics Model Mesh Convergence Tests}
  \begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{diffusion-mesh-convergence-k}
      \caption{Neutron diffusion method}
      \label{fig:diff-mesh-k}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{sn-mesh-convergence-k}
      \caption{$S_8$ neutron transport method}
      \label{fig:sn-mesh-k}
    \end{subfigure}
    \caption{Convergence of multiplication factor ($k_\text{eff}$) estimates for Case 3b across four
      levels of mesh refinement relative to the finest mesh resolution.}
    \label{fig:mesh-k}
  \end{figure}
\end{frame}

@@

\begin{frame}[noframenumbering]
  \begin{figure}[t]
    \centering
    \includegraphics[width=.5\columnwidth]{case-3b-drift}
    \caption{Multigroup drift correction ($\vec{D}_g$) $x$-component distributions from the
    Moltres-hybrid and Moltres-$S_8$ solvers.}
    \label{fig:3b-drift}
  \end{figure}
\end{frame}

@@

\begin{frame}[noframenumbering]
  \begin{columns}
    \column{5.5cm}
    \begin{figure}[t]
      \small
      \centering
      \includegraphics[width=.75\columnwidth]{ray-effect-12}
      \caption{Group 1 and 2 neutron flux distributions in the hybrid $S_N$-diffusion method correction
      region with $S_6$, $S_8$, $S_{10}$, \& $S_{12}$.}
      \label{fig:ray-effect-12}
    \end{figure}
    \column{5.5cm}
    \begin{figure}[t]
      \small
      \centering
      \includegraphics[width=.75\columnwidth]{ray-effect-34}
      \caption{Group 3 and 4 neutron flux distributions in the hybrid $S_N$-diffusion method correction
      region with $S_6$, $S_8$, $S_{10}$, \& $S_{12}$.}
      \label{fig:ray-effect-34}
    \end{figure}
  \end{columns}
\end{frame}

@@

\begin{frame}[noframenumbering]
  \begin{figure}[t]
    \centering
    \includegraphics[width=.6\columnwidth]{3d-view-high-res}
    \caption{3-D section view of the \gls{MSRE} model geometry with Rod 1 inserted by 4.4 inches at
    initial criticality.}
    \label{fig:3d-view}
  \end{figure}
\end{frame}

\begin{frame}[noframenumbering]
  \begin{figure}[t]
    \centering
    \includegraphics[width=.6\columnwidth]{ic-g1}
    \caption{Group 1 neutron flux distribution with Rod 1 inserted by 4.4 inches at initial
    criticality.}
    \label{fig:ic-g1}
  \end{figure}
\end{frame}

\begin{frame}[noframenumbering]
  \begin{figure}[t]
    \centering
    \includegraphics[width=.6\columnwidth]{ic-g8}
    \caption{Group 8 neutron flux distribution with Rod 1 inserted by 4.4 inches at initial
    criticality.}
    \label{fig:ic-g8}
  \end{figure}
\end{frame}

@@

\begin{frame}[noframenumbering]
  \frametitle{MSRE Rod Drop Simulation Interpolated Results}
  \begin{columns}
    \column{5.5cm}
    \centerline{\large \textbf{Neutron Count Rate}}
    \begin{figure}[t]
      \centering
      \includegraphics[width=\columnwidth]{count-rate-interp}
      \caption{Neutron count rate during the rod drop experiment with linearly
      interpolated data between $t=1.325$ s and $t=3.825$ s.}
      \label{fig:count-rate}
    \end{figure}
    \column{5.5cm}
    \centerline{\large \textbf{Integral Neutron Count}}
    \begin{figure}[t]
      \centering
      \includegraphics[width=\columnwidth]{integral-count-interp}
      \caption{Integral neutron count during the rod drop experiment with linearly interpolated
      count rate data between $t=1.325$ s and $t=3.825$ s.}
      \label{fig:count-rate}
    \end{figure}
  \end{columns}
\end{frame}

\begin{frame}[noframenumbering]
  \frametitle{Rod Cusping Correction}
  \begin{figure}[t]
      \centering
      \begin{subfigure}[t]{.49\textwidth}
          \centering
          \includegraphics[width=\textwidth]{rod-cusping-1}
          \caption{Uncorrected volume weighting}
          \label{fig:rod-cusping-1}
      \end{subfigure}
      \hfill
      \begin{subfigure}[t]{.49\textwidth}
          \centering
          \includegraphics[width=\textwidth]{rod-cusping-2}
          \caption{Corrected volume weighting}
          \label{fig:rod-cusping-2}
      \end{subfigure}
      \caption{Fraction of reactivity change against control rod volume fraction in mixed mesh
      elements with the rod inserted at mid-reactor height (27.4 to 29.4 inches) and full insertion
      height (0.0 to 1.9 inches).}
      \label{fig:rod-cusping}
  \end{figure}
\end{frame}

### 2024-12-12 presentation/conclusion.tex
slide edits

%\begin{frame}
%  \frametitle{Conclusion}
%  \begin{block}{\textbf{Objectives}}
%    \begin{enumerate}
%      \item \textbf{Improve Multiphysics Capabilities in Moltres}
%      \begin{itemize}
%        \item \textbf{Verify and Validate Existing Multiphysics Coupling Capabilities in Moltres}
%        \item \textbf{Implement a RANS-based Turbulence Model in Moltres}
%      \end{itemize}
%      \item \textbf{Develop a Hybrid Neutronics Method for Control Rod Modeling in Moltres}
%    \end{enumerate}
%  \end{block}
%  \begin{block}{\textbf{Research Impact}}
%    \begin{itemize}
%      \item \textbf{Improve Moltres as a simulation tool for MSR multiphysics modeling}
%      \item \textbf{Allow for a wider range of MSR simulation scenarios on Moltres involving
%        turbulent flow and control rod movement}
%      \item \textbf{Analysis of neutron transport effects in MSRs that are neglected by neutron
%        diffusion methods}
%%      \item \textbf{Publication of numerical data for MSRE control rod insertion/withdrawal
%%        simulations}
%    \end{itemize}
%  \end{block}
%\end{frame}

\begin{frame}
  \frametitle{Conclusion}
  \begin{block}{\textbf{Moltres Multiphysics V\&V Studies}}
    \textbf{Relevance}
    \begin{itemize}
      \item Existing multiphysics coupling capabilities in Moltres must be verified and validated
    \end{itemize}
    \textbf{Results Presented}
    \begin{itemize}
      \item CNRS numerical benchmark study with Moltres (Dissertation)
      \item MSRE pump transient V\&V study with Moltres
    \end{itemize}
    \textbf{Major takeaways}
    \begin{itemize}
      \item Moltres is highly consistent with other MSR simulation tools in accurately modeling:
      \begin{itemize}
        \item Salt flow-induced temperature and DNP drift
        \item Temperature ractivity feedback due to Doppler broadening and thermal expansion
        \item Buoyancy-driven flow due to temperature gradients
        \item Time-varying and looped precursor flow
      \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{Conclusion}
  \begin{block}{\textbf{Spalart-Allmaras Turbulence Model Implementation in Moltres}}
    \textbf{Relevance}
    \begin{itemize}
      \item Moltres requires turbulence modeling capability to model turbulent salt
        flow in MSRs
    \end{itemize}
    \textbf{Results Presented}
    \begin{itemize}
      \item Implementation of a Spalart-Allmaras turbulence model in Moltres
      \item V\&V studies of turbulent channel, turbulent pipe, and backward-facing step flow
    \end{itemize}
    \textbf{Major Takeaways}
    \begin{itemize}
      \item The Spalart-Allmaras turbulence model in Moltres is accurate for turbulent channel and
        pipe flows
      \item It is also consistent with other implementations when simulating the
        backward-facing step flow problem.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{Conclusion}
  \begin{block}{\textbf{Hybrid $\bm{S_N}$-Diffusion Method}}
    \textbf{Relevance}
    \begin{itemize}
      \item There are no MSR simulation tools or studies that explicitly model moving control rods.
    \end{itemize}
    \textbf{Results Presented}
    \begin{itemize}
      \item Development and implementation of a hybrid $S_N$-diffusion method for
        accurate control rod modeling in Moltres
      \item Verification, validation, and demonstration of the hybrid $S_N$-diffusion
        method through 1-D, 2-D, \& 3-D analyses of the MSRE
    \end{itemize}
    \textbf{Major Takeaways}
    \begin{itemize}
      \item The hybrid method is an iterative method that applies a $S_N$ subsolver around control
        rod regions for improved rod worth estimates
      \item The hybrid method applies an adaptive boundary coupling between
        the $S_N$ subsolver and the neutron diffusion solver to smooth flux gradients
      \item The hybrid method accurately reproduces control rod worths at only four times the
        computational cost of the neutron diffusion method
      \item The hybrid method exhibits good scalability on high-performance computing clusters
    \end{itemize}
  \end{block}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Conclusion}
  \begin{block}{\textbf{Moltres Multiphysics V\&V Studies}}
    \textbf{Relevance}
    \begin{itemize}
      \item Existing multiphysics coupling capabilities in Moltres must be verified and validated.
    \end{itemize}
    \textbf{Results Presented}
    \begin{itemize}
      \item CNRS numerical benchmark study with Moltres (Dissertation)
      \item MSRE pump transient V\&V study with Moltres
    \end{itemize}
    \textbf{Major takeaways}
    \begin{itemize}
      \item Moltres is highly consistent with other MSR simulation tools in accurately modeling:
      \begin{itemize}
        \item Salt flow-induced temperature and DNP drift
        \item Temperature ractivity feedback due to Doppler broadening and thermal expansion
        \item Buoyancy-driven flow due to temperature gradients
        \item Time-varying and looped precursor flow
      \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{Conclusion}
  \begin{block}{\textbf{Spalart-Allmaras Turbulence Model Implementation in Moltres}}
    \textbf{Relevance}
    \begin{itemize}
      \item Moltres requires turbulence modeling capability to model turbulent salt
        flow in MSRs.
    \end{itemize}
    \textbf{Results Presented}
    \begin{itemize}
      \item Implementation of a Spalart-Allmaras turbulence model in Moltres
      \item V\&V studies of turbulent channel, turbulent pipe, and backward-facing step flow
    \end{itemize}
    \textbf{Major Takeaways}
    \begin{itemize}
      \item The Spalart-Allmaras turbulence model in Moltres is accurate for turbulent channel and
        pipe flows.
      \item It is also consistent with other implementations when simulating the
        backward-facing step flow problem.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{Conclusion}
  \begin{block}{\textbf{Hybrid $\bm{S_N}$-Diffusion Method}}
    \textbf{Relevance}
    \begin{itemize}
      \item There are no MSR simulation tools or studies that explicitly model moving control rods.
    \end{itemize}
    \textbf{Results Presented}
    \begin{itemize}
      \item Development and implementation of a hybrid $S_N$-diffusion method for
        accurate control rod modeling in Moltres
      \item Verification, validation, and demonstration of the hybrid $S_N$-diffusion
        method through 1-D, 2-D, \& 3-D analyses of the MSRE
    \end{itemize}
    \textbf{Major Takeaways}
    \begin{itemize}
      \item The hybrid method is an iterative method that applies a $S_N$ subsolver around control
        rod regions for improved rod worth estimates.
      \item The hybrid method applies an adaptive boundary coupling between
        the $S_N$ subsolver and the neutron diffusion solver to smooth flux gradients.
      \item The hybrid method accurately reproduces control rod worths at only four times the
        computational cost of the neutron diffusion method.
      \item The hybrid method exhibits good scalability on high-performance computing clusters.
    \end{itemize}
  \end{block}
\end{frame}

### 2024-12-12 presentation/review.tex
slide edits

\begin{frame}
  \frametitle{Transport-Correction Techniques For Neutron Diffusion-Based Solvers}
  Techniques for augmenting the neutron diffusion method (or equivalent low-order equations) with
  corrections derived from neutron transport:
  \begin{itemize}
    \item Ronen method \cite{ronen_accurate_2004, tomatis_ronen_2021, gross_comprehensive_2023}
    \item Multilevel quasi-diffusion method \cite{goldin_quasi-diffusion_1964, tamang_multilevel_2014, reynolds_analysis_2023}
    \item Multischeme transport method \cite{wang_hybrid_2017}
    \item Hybrid transport-diffusion method \cite{anistratov_computational_2012, stehle_hybrid_2014}
  \end{itemize}
  These techniques generally require:
  \begin{itemize}
    \item High-order neutron transport solver
    \item Corrective terms for the neutron diffusion equations
    \item Boundary coupling scheme (for spatial domain decomposition)
  \end{itemize}
\end{frame}

@@

  Reynolds \& Palmer applied the same approach for steady-state simulations of a 2-D axisymmetric,
  two-group MSRE model \cite{reynolds_analysis_2023}.
  %
  \begin{figure}[h]
    \centering
    \includegraphics[width=.6\columnwidth]{images/reynolds-flux}
    \caption{Fast and thermal fluxes of the 2-D axisymmetric MSRE model by Reynolds \& Palmer
    \cite{reynolds_analysis_2023}.}
    \label{fig:reynolds-flux}
  \end{figure}
  \textbf{Limitation: Computational expensive for 3-D full-core simulations.}
\end{frame}

@@

  It uses two-level neutronics method based on the Second-Moment method \cite{lewis_comparison_1976}.
  The low-order second-moment equations on the $(s+1)$th iteration are:
  \begin{gather}
    \nabla\cdot J^{(s+1)}+\Sigma_a\phi^{(s+1)} = q, \label{eq:2nd-moment-1} \\
    \frac{1}{3}\nabla\cdot\phi^{(s+1)}+\Sigma_t J^{(s+1)} = \nabla\cdot F^{(s+1/2)}
    \label{eq:2nd-moment-2}
    \shortintertext{where}
    F^{(s+1/2)}_{\alpha\beta} = \int_{4\pi}
    \left(\frac{1}{3}\delta_{\alpha\beta}-\Omega_\alpha\Omega_\beta\right)
    \Psi^{(s+1/2)} d\Omega \label{eq:2nd-moment-3}
  \end{gather}
  %
  The transport subdomains require interface conditions in the form of boundary sources from
  neighboring diffusion subdomains.

@@

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: Literature Review}
  \begin{block}{\textbf{Summary}}
    \begin{itemize}
      \item Corrective terms for the neutron diffusion equations in various forms have been
        effectively applied across various methods.
      \item Domain decomposition is necessary for limiting computational cost in large 3-D reactor
        simulations.
      \item Interface conditions are required when applying domain decomposition to iteratively
        couple the transport and diffusion solvers.
%      \item Demonstrations of the Ronen method are limited to 1-D geometries due to the difficulty of
%        deriving transport operators for complex 2-D and 3-D geometries
    \end{itemize}
  \end{block}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Literature Review}
  \textbf{Transport-Correction Techniques For Neutron Diffusion-Based Solvers}
  \vspace{.2cm}

  Techniques for augmenting the neutron diffusion method (or equivalent low-order equations) with
  corrections derived from neutron transport:
  \begin{itemize}
    \item Ronen method \cite{ronen_accurate_2004, tomatis_ronen_2021, gross_comprehensive_2023}
    \item Multilevel quasi-diffusion method \cite{goldin_quasi-diffusion_1964, tamang_multilevel_2014, reynolds_analysis_2023}
    \item Multischeme transport method \cite{wang_hybrid_2017}
    \item Hybrid transport-diffusion method \cite{anistratov_computational_2012, stehle_hybrid_2014}
  \end{itemize}
  These techniques generally require:
  \begin{itemize}
    \item High-order neutron transport solver
    \item Corrective terms for the neutron diffusion equations
    \item Boundary coupling scheme (for spatial domain decomposition)
  \end{itemize}
\end{frame}

@@

  Reynolds \& Palmer applied the same approach for steady-state simulations of a 2-D axisymmetric,
  two-group MSRE model \cite{reynolds_analysis_2023}.
  %
  \begin{figure}[h]
    \centering
    \includegraphics[width=.6\columnwidth]{images/reynolds-flux}
    \caption{Fast and thermal fluxes of the 2-D axisymmetric MSRE model by Reynolds \& Palmer
    \cite{reynolds_analysis_2023}.}
    \label{fig:reynolds-flux}
  \end{figure}
  \textbf{Limitation: Computationally expensive for 3-D full-core simulations.}
\end{frame}

@@

  It uses two-level neutronics method based on the Second-Moment method \cite{lewis_comparison_1976}.
  The low-order second-moment equations on the $(s+1)$th iteration are:
  \begin{gather}
    \nabla\cdot J^{(s+1)}+\Sigma_a\phi^{(s+1)} = q, \label{eq:2nd-moment-1} \\
    \frac{1}{3}\nabla\cdot\phi^{(s+1)}+\Sigma_t J^{(s+1)} = \nabla\cdot F^{(s+1/2)}
    \label{eq:2nd-moment-2}
    \shortintertext{where}
    F^{(s+1/2)}_{\alpha\beta} = \int_{4\pi}
    \left(\frac{1}{3}\delta_{\alpha\beta}-\Omega_\alpha\Omega_\beta\right)
    \Psi^{(s+1/2)} d\Omega \label{eq:2nd-moment-3}
  \end{gather}
  %
  The transport subdomains require interface conditions in the form of boundary sources from
  neighboring diffusion subdomains.
  \vspace{.2cm}

@@

\begin{frame}
  \frametitle{Literature Review}
  \begin{block}{\textbf{Summary}}
    \begin{itemize}
      \item Corrective terms for the neutron diffusion equations in various forms have been
        effectively applied across various methods.
      \item Domain decomposition is necessary for limiting computational cost in large 3-D reactor
        simulations.
      \item Interface conditions are required when applying domain decomposition to iteratively
        couple the transport and diffusion solvers.
%      \item Demonstrations of the Ronen method are limited to 1-D geometries due to the difficulty of
%        deriving transport operators for complex 2-D and 3-D geometries
    \end{itemize}
  \end{block}
\end{frame}

### 2024-12-12 presentation/turb-moltres.tex
slide edits

@@

\begin{frame}
  \frametitle{Spalart-Allmaras Turbulence Model in Moltres}
  \textbf{Spalart-Allmaras Model with Rotation Correction Scheme
  \cite{spalart_one-equation_1994, aupoix_extensions_2003, dacles-mariani_numericalexperimental_1995}}\\
  \\
  Governing equation for the modified dynamic viscosity, $\tilde{\mu}$:
  \begin{multline}
    \rho \frac{\partial\tilde{\mu}}{\partial t} + \rho \mathbf{u}\cdot\nabla\tilde{\mu} = \rho c_{b1}
    \left(1-f_{t2}\right)\tilde{S}\tilde{\mu} + \frac{1}{\sigma}\{\nabla\cdot\left[\left(\mu+
    \tilde{\mu}\right)\nabla\tilde{\mu}\right] + c_{b2}|\nabla\tilde{\mu}|^2\} \\
    - \left(c_{w1}f_w - \frac{c_{b1}}{\kappa^2}f_{t2}\right)\left(\frac{\tilde{\mu}}{d}\right)^2
  \end{multline}
  \begin{align*}
    \shortintertext{where}
      \mu_t &= \tilde{\mu}f_{v1} = \text{turbulent eddy viscosity}, \\
      f_{v1} &= \frac{\chi^3}{\chi^3 + c_{v1}^3}, \\
      \chi &= \frac{\tilde{\mu}}{\mu}.
  \end{align*}
%      \tilde{S} &= \Omega + \frac{\tilde{\nu}}{\kappa^2 d^2} f_{v2}, \\
%      f_{v2} &= 1 - \frac{\chi}{1+\chi f_{v1}}, \\
%      \Omega &= \sqrt{2W_{ij}W_{ij}} = \text{vorticity magnitude}, \\
%      W_{ij} &= \frac{1}{2}\left(\frac{\partial u_i}{\partial x_j} - \frac{\partial u_j}{\partial x_i}
%      \right), \\
%        f_w &= g\left(\frac{1 + c_{w3}^6}{g^6 + c_{w3}^6}\right)^{1/6}, \\
%        g &= r + c_{w2}\left(r^6 - r\right), \\
%        r &= \text{min}\left(\frac{\tilde{\nu}}{\tilde{S}\kappa^2d^2}, 10\right), \\
%        f_{t2} &= c_{t3} \exp{\left(-c_{t4}\chi^2\right)},
%    \end{align*}
%  \shortintertext{and the constants are}
%    \sigma = \frac{2}{3}, \ c_{b1} = 0.1355, \ c_{b2} = 0.622, \ \kappa = 0.41, \
%    c_{w1} = \frac{c_{b1}}{\kappa^2} + \frac{1+c_{b2}}{\sigma}, \nonumber \\
%    c_{w2} = 0.3, \ c_{w3} = 2, \
%    c_{v1} = 7.1, \ c_{t3} = 1.2, \ c_{t4} = 0.5 \ \text{.} \nonumber
\end{frame}

@@

\begin{frame}
  \frametitle{Backward-Facing Step Flow Validation Test Setup}
  \begin{columns}
    \column{5.5cm}
    \begin{figure}[h]
      \centering
      \includegraphics[width=\columnwidth]{backstep-geom-pres}
      \caption{Backward step geometry for the turbulent BFS flow verification test. The red box indicates
      the region shown by the close-up view in Figure \ref{fig:bfs-mesh}.}
      \label{fig:backstep-geom}
    \end{figure}
    \column{5.5cm}
    \begin{figure}[h]
      \centering
      \includegraphics[width=\columnwidth]{bfs_mesh}
      \caption{Close-up view of the mesh for the BFS flow test. The step is situated at $x=110$ m
      with a height of $H=1$ m.}
      \label{fig:bfs-mesh}
    \end{figure}
  \end{columns}
\end{frame}

>>>>

%\begin{frame}
%  \frametitle{Spalart-Allmaras Turbulence Model in Moltres}
%  \begin{block}{\textbf{Why the Spalart-Allmaras Model \cite{spalart_one-equation_1994} for Moltres?}}
%    A computationally efficient one-equation model that provides reasonable estimates for wall-bounded
%    turbulent flows and is tractable for large problems on small computing clusters.
%  \end{block}
%  \textbf{Spalart-Allmaras Model with Rotation Correction Scheme
%  \cite{spalart_one-equation_1994, aupoix_extensions_2003, dacles-mariani_numericalexperimental_1995}}\\
%  \\
%  Governing equation for the modified dynamic viscosity, $\tilde{\mu}$:
%  \begin{multline}
%    \rho \frac{\partial\tilde{\mu}}{\partial t} + \rho \mathbf{u}\cdot\nabla\tilde{\mu} = \rho c_{b1}
%    \left(1-f_{t2}\right)\left[\tilde{S}+C_\text{rot}\min(0,S-\Omega)\right]\tilde{\mu} \\ + \frac{1}{\sigma}\{\nabla\cdot\left[\left(\mu+
%    \tilde{\mu}\right)\nabla\tilde{\mu}\right] + c_{b2}|\nabla\tilde{\mu}|^2\}
%    - \left(c_{w1}f_w - \frac{c_{b1}}{\kappa^2}f_{t2}\right)\left(\frac{\tilde{\mu}}{d}\right)^2
%  \end{multline}
%  \begin{align*}
%    \shortintertext{where}
%      \mu_t &= \tilde{\mu}f_{v1} = \text{turbulent eddy viscosity}, \\
%      f_{v1} &= \frac{\chi^3}{\chi^3 + c_{v1}^3}, \\
%      \chi &= \frac{\tilde{\mu}}{\mu}.
%  \end{align*}
%\end{frame}

@@

\begin{frame}
  \frametitle{Spalart-Allmaras Turbulence Model in Moltres}
  \textbf{Spalart-Allmaras Model with Rotation Correction Scheme
  \cite{spalart_one-equation_1994, aupoix_extensions_2003, dacles-mariani_numericalexperimental_1995}}\\
  \\
  Governing equation for the modified dynamic viscosity, $\tilde{\mu}$:
  \begin{multline}
    \rho \frac{\partial\tilde{\mu}}{\partial t} + \rho \mathbf{u}\cdot\nabla\tilde{\mu} = \rho c_{b1}
    \left(1-f_{t2}\right)\left[\tilde{S}+C_\text{rot}\min(0,S-\Omega)\right]\tilde{\mu} \\ + \frac{1}{\sigma}\{\nabla\cdot\left[\left(\mu+
    \tilde{\mu}\right)\nabla\tilde{\mu}\right] + c_{b2}|\nabla\tilde{\mu}|^2\}
    - \left(c_{w1}f_w - \frac{c_{b1}}{\kappa^2}f_{t2}\right)\left(\frac{\tilde{\mu}}{d}\right)^2
  \end{multline}
  \begin{align*}
    \shortintertext{where}
      \mu_t &= \tilde{\mu}f_{v1} = \text{turbulent eddy viscosity}, \\
      f_{v1} &= \frac{\chi^3}{\chi^3 + c_{v1}^3}, \\
      \chi &= \frac{\tilde{\mu}}{\mu}.
  \end{align*}
\end{frame}

@@

%\begin{frame}
%  \frametitle{Backward-Facing Step Flow Validation Test Setup}
%  \begin{columns}
%    \column{5.5cm}
%    \begin{figure}[h]
%      \centering
%      \includegraphics[width=\columnwidth]{backstep-geom-pres}
%      \caption{Backward step geometry for the turbulent BFS flow verification test. The red box indicates
%      the region shown by the close-up view in Figure \ref{fig:bfs-mesh}.}
%      \label{fig:backstep-geom}
%    \end{figure}
%    \column{5.5cm}
%    \begin{figure}[h]
%      \centering
%      \includegraphics[width=\columnwidth]{bfs_mesh}
%      \caption{Close-up view of the mesh for the BFS flow test. The step is situated at $x=110$ m
%      with a height of $H=1$ m.}
%      \label{fig:bfs-mesh}
%    \end{figure}
%  \end{columns}
%\end{frame}
